Difficult Text Analysis of Machine Translation Services base on Metamorphic Testing in Social Media

### 2019-01-23 icse/paper.tex
backup

\section{Background}
\subsection{Metamorphic Testing}
Metamorphosis Testing(MT) a method for generating test cases, as well as test
results verification. The most importance component is the metamorphic
relation(MR). MR is the target application's necessary properties of function in relation to multiple
inputs and their expected outputs. When people want to assess the
the accuracy of $\sin$ function. For example, $\sin(2.7)$ is very difficult to
make a correctness judgment from mathematics aspect. If using Metamorphic
Testing method to testing $\sin$ function will reduce computational costs and
more efficient.
\begin{enumerate}
\item set a Metamorphic relation: such as $\sin(\alpha) = \cos(\frac{\pi}{2} - \alpha)$
\item

\end{enumerate}
However, when using
Metamorphic Testing method set a metamorphic relation, which is  will less cost . If  make a correctness judgment

which are expected relations among the inputs and
outputs of multiple executions of the intended program’s functionality.

are an approach for generating both test cases and test results. A central element is a set of metamorphosis
relationships, which are necessary properties of the objective function or the algorithm in relation to multiple inputs and their expected
outputs.

Since its first publication, we have witnessed a rapidly increasing body of work examining metamorphic testing from
various perspectives, including metamorphic relation identification, test case generation, integration with other software engineering
techniques, and the validation and evaluation of software systems.

>>>>

\section{Background}
\subsection{Metamorphic Testing}
Metamorphosis Testing(MT) a method for generating test cases, as well as test
results verification. The most importance component is the metamorphic
relation (MR). MR is the target application's necessary properties of function in relation to multiple
inputs and their expected outputs.
In software testing research field, an incapacity to decide, software product
the correct output, is called the oracle problem. This usually means cannot
provide exact correctness reference data. such as, machine translation. Huge and
complexity systems is very common, no
When people want to assess the the accuracy of $\sin$ function. For example, $\sin(2.7)$ is very difficult to
make a correctness judgment from mathematics aspect. If using Metamorphic
Testing method to testing $\sin$ function will reduce computational costs and
more efficient. There is a testing procedures' example for $\sin$ function.
\begin{enumerate}\label{itm:procedures}
\item set a Metamorphic Relation: such as $$\sin(\alpha) = \cos(\frac{\pi}{2} - \alpha)$$
\item $\sin(2.7)$ and $\cos(\frac{\pi}{2} - 2.7)$ should have same output, if the
  outputs are different. We can say, the failure have been detected.
\end{enumerate}
However, when using \ref{itm:procedures}'s testing procedures. someone maybe
ask, $\cos$ function also not reliable, how can use a unreliable function to
test another function's correctness. There have the boundedness. However, both
function have got failures at same time, that is small probability event.
